Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
j

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +        
       ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))

@@

  if (catalogue == "Fennica") {
    df <- df.full # full time span
  } else if (catalogue == "Kungliga") {
    df <- df.full # full time span
  }
  langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
  df <- df %>% filter(catalog == catalogue)%>%
        filter(publication_year >= 1600 & publication_year <= 1900)

@@

  df <- df0 %>% filter(catalog == catalogue) %>%
        filter(publication_year >= 1600 & publication_year <= 1828)

@@

>>>>

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +        
       ggtitle(paste("Unique publishers in selected publication places"))

@@

  if (catalogue == "Fennica") {
    df <- df.full # full time span
  } else if (catalogue == "Kungliga") {
    df <- df.full # full time span
  }
  langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Danish", "English", "Other")
  df <- df %>% filter(catalog == catalogue)%>%
        filter(publication_year >= 1640 & publication_year <= 1900)

@@

  df <- df0 %>% filter(catalog == catalogue) %>%
        filter(publication_year >= 1640 & publication_year <= 1828)

@@

[University curriculum & Enlightenment in Finland]
TODO: UUSI SLIDE top-authors publishing in octavo (title count) Fennica and Kungliga. OF COURSE!
